comgen-outline

### 2017-12-21 paper/case1-generics.Rmd
play around with plots, edits to habituals fixed model results

<!-- Accurately modeling the prior data is important to generate precise quantitative predictions about endorsement. -->
In order to integrate the results of this prior measurement task into our model of endorsement, we must accurately model the prior elicitation data.
We do this using a Bayesian mixture model, which assumes that the data generated for each property (e.g., \textsc{lay eggs}) comes from one of two underlying Beta distributions (*Mixture of Betas*).^[
  The Beta distribution is chosen because the support of this distribution is numerical values between 0 - 1, exactly the form of the response data in the prior elicitation task.
] 
We specify one of these distributions *a priori* to represent kinds of animals who *do not have* a stable causal mechanism that could give rise to the property (e.g., \textsc{lions} and \textsc{lay eggs}), which results in prevalence or prevalence values close to or equal to 0.
This "null distribution" is potentially present for all features in exactly the same way.
The second distribution represents kinds of animals who *do have* such a mechanism, and the two parameters of this distribution are not specified *a priori* and are not the same for all properties, but are inferred on a property-wise basis from participants' responses.
The *Mixture of Betas* distribution has a third free parameter (for each property), the relative contribution of the "null distribution" (for example: we expect the "null distribution" to not contribute at all to properties like *being female*, for which almost all categories have at least some members with the property).
To ensure the *Mixture of Betas* model of the prior is not overly complex, we fit an additional model that represents only a single underlying distribution (*Single Beta*) for a comparison.
<!-- is flexible and can represent different shapes for different properties (e.g., the differences in prevalence judgments for \textsc{lay eggs} vs. \text{has wings}). -->
For more details about model implementation and inference, see Appendix.

@@

  # for (c in 1:2){
  #     m.gen.endorse.priors.savage <- webppl(
  #   paste(genericEndorsementPriorModelHelpers, 
  #         savageDickeyModel, sep = '\n'), 
  #   data = priorData, 
  #   data_var = "data"
  #   )

  # m.inferred.prior <- get_samples(
  #   data.frame(m.gen.endorse.priors.savage$prior) %>%
  #     rename(prob = probs), n_samples)
  # 
  # m.inferred.posterior <- get_samples(
  #   data.frame(m.gen.endorse.priors.savage$posterior) %>%
  #     rename(prob = probs), n_samples)
  # 
  # posterior.density <- density(m.inferred.posterior$phi,
  #         from = 0, to = 1)
  # 
  # prior.density <- density(m.inferred.prior$phi,
  #         from = 0, to = 1)
  # 
  # logBF01 = log(approxfun(posterior.density)(1)) - 
  #   log(approxfun(prior.density)(1))

  # m.gen.endorse.priors.savage.summary <- bind_rows(
  #   m.gen.endorse.priors.savage.summary,
  #     bind_rows(
  #     data.frame(Property = p, 
  #                Chain = c, 
  #                diff = NA,
  #                logBF01 = logBF01,
  #                BF01= exp(logBF01)),
  #     data.frame(m.gen.endorse.priors.savage$logBFs) %>%
  #       rename(diff = X1, logBF01 = X2) %>%
  #       mutate(Property = p, Chain = c, BF01 = exp(logBF01))
  #     )
  # )
  # 
  # }

    #for (c in 1:3){

      # posterior.logspline <-  polspline::logspline(filter(
      #   m.gen.endorse.priors, Parameter == 'phi', Chain == c)$value,
      #   lbound = 0, ubound = 1)
      # 
      #   posterior <- dlogspline(1, posterior.logspline)
      # prior <- dunif(1, min = 0, max = 1)
      # BF01 <- posterior/prior
      # 
      # print(log(BF01))

  #}

  #print(p)
  #print(priorData)
}
save(m.gen.endorse.priors.posteriorPredictive, file = '../analysis/generics-priors-posteriorPredictives.Rdata')

@@

gen.priors.cdfs <-m.gen.endorse.priors.posteriorPredictive %>%
  mutate(src = factor(src, levels = c("Data", "Structured", "Unstructured"),
                      labels = c("Empirical distribution", 
                                 "Mixture of Betas",
                                 "Single Beta"))) %>%
ggplot(.,
           aes( x = prevalence, color = src, lty = src))+
    #geom_density(aes(y = ..scaled..), adjust = 1.3, size = 1)+
    #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    stat_ecdf(size = 1)+
    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_alpha_manual(values = c(0.6, 0.4, 0))+
    facet_wrap(~Property, nrow = 2)+
    scale_linetype_manual(values = c(1, 4, 3))+
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    #coord_fixed()+
    xlab("prevalence") +
    ylab("Cumulative probability density")+
    theme(legend.title = element_blank(), legend.position = 'bottom')

@@

```{r generic-RSAmodels, fig.width = 8}
n_chains <- 3
n_samples <- 100000
burn <- n_samples / 2
lg <- 20

model_prefix <- "results-generics-jointModel-S1-smntcs_"
#fixed_model_prefix <- "results-generics-jointModel-wNoise-inferFixedThreshold-20bins-S1-smntcs_some-"
# m.samp <- data.frame()
# m.samp.fixed <- data.frame()
#for (i in seq(1, n_chains)){
  #mi.gen <- fread(paste(project.path,  "models/generics/results/", model_prefix, "generic-",
  #                  n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
  #m.samp <- bind_rows(m.samp, mi.gen %>% mutate(chain = i))

#   mi.fixed <- fread(paste(project.path,  "models/generics/results/", fixed_model_prefix,
#                     n_samples, "_burn", burn, "_lag", lg ,"_chain", i, ".csv", sep = ""))
#   m.samp.fixed <- bind_rows(m.samp.fixed, mi.fixed %>% mutate(chain = i))
# }
# 
# save(m.samp,
#      file = paste(project.path,  "models/generics/results/", model_prefix, "generic-",
#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
# 
# save(m.samp.fixed,
#      file = paste(project.path,  "models/generics/results/", model_prefix, "some-",
#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))

@@

# load(file = paste(project.path,  "models/generics/results/", model_prefix, "some-",
#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
load(file = paste(project.path, "models/generics/results/results-generics-jointModel-S1-some-inferFixedThreshold-noise-100000_burn50000_lag20_2chains.RData", sep = ""))

@@

@@

```{r generic-model-scatters}
m.gen.endorse.rsa <- bind_rows(
  left_join(
    d.gen.endorse.bayes,
    m.gen.fullmodel.endorsement %>%
      mutate(sentence = paste(category, " ", property, ".", sep = "")) %>%
      ungroup() %>%
      select(-type, -param)
  ) %>%
    mutate(src = "generics_model"),
  left_join(
    d.gen.endorse.bayes,
    m.gen.somemodel.endorsement %>%
      mutate(sentence = paste(category, " ", property, ".", sep = "")) %>%
      ungroup() %>%
      select(-type, -param)
  ) %>%
    mutate(src = "some_model")
)

@@

generics.endorsement.models <- bind_rows(
  d.gen.endorse.regression,
  left_join(
    m.gen.endorse.rsa %>% 
      rename(prediction_mean = MAP, prediction_ci_lower = cred_lower, prediction_ci_upper = cred_upper),
    d.gen.endorse.regression %>% 
      select(sentence, Property, Category, prev_mean, cv_mean)
  )
) %>%
  mutate(src = factor(src, levels = c( "some_model",
                                      "generics_model",

                                      "regression_Prev", 
                                      "regression_Prev_Cuevalidity"
                                     ),
                      labels = c("Fixed semantics model",
                                 "Uncertain semantics model",

                                 "Prevalence",
                                 "Cue validity + Prevalence"
                                 ))) %>%
  ggplot(., aes ( x = prediction_mean, xmin = prediction_ci_lower, xmax = prediction_ci_upper,
                  y = MAP_h, ymin = low, ymax = high, fill = prev_mean ))+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  geom_linerange(alpha = 0.4)+
  geom_errorbarh(alpha = 0.4)+
  geom_point(shape = 21, size = 3)+
  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
  coord_fixed()+
  xlab("Model prediction")+
  ylab("Human generic endorsement")+
  facet_wrap(~src, nrow = 2)+
  #theme(legend.position = "bottom")+
  guides(fill = F)
```

```{r generic-model-insets, fig.width = 4.75, fig.height = 1.5}
example.generics.properties <- c("dont eat people", 
                      "carry malaria", 
                      "lay eggs", 
                      "are female",
                      "have spots")

example.generics <- c("Tigers dont eat people", 
                      "Mosquitos carry malaria", 
                      "Robins lay eggs", 
                      "Robins are female",
                      "Leopards have spots")

@@

To evaluate the fixed-threhsold model, we examine the posterior distribution which represents what we should believe about the latent parameters of the model (referent prevalence, prevalence priors, the optimality, fixed-threshold, and noise parameters) given the observed data, as well as what predictions of the model given these parameter values.
The Maximum A-Posteriori value and 95\% highest probability density interval for the inferred (fixed) threshold and noise parameters are `r round(fixed.threshold.posterior[[1,"MAP"]], 2)` [`r round(fixed.threshold.posterior[[1,"cred_lower"]], 2)`,
`r round(fixed.threshold.posterior[[1,"cred_upper"]], 2)`] and `r round(generics.fixed.noise.posterior[[1,"MAP"]], 2)` [`r round(generics.fixed.noise.posterior[[1,"cred_lower"]], 2)`,
`r round(generics.fixed.noise.posterior[[1,"cred_upper"]], 2)`], respectively.
Importantly, the model recapitulates the prior elicitation data (e.g., the probability of laying eggs among various species) and the referent-category prevalence data (e.g., the probability of laying eggs among robins) as it did when the Bayesian data analysis model only included these data and their associated model (results section of Expt. 1b).
This result confirms that the theoretically-interesting predictions of this model --- predictions of generic endorsement --- are based on intuitively meaningful model components (i.e., the shapes of the prevalence distributions).

@@

>>>>

<!-- Accurately modeling the prior data is important to generate precise quantitative predictions about endorsement. -->
In order to integrate the results of this prior measurement task into our model of endorsement, we must accurately model the prior elicitation data.
We do this using a Bayesian mixture model, which assumes that the data generated for each property (e.g., \textsc{lay eggs}) comes from one of two underlying Beta distributions (*Mixture of Betas*).^[
  The Beta distribution is chosen because the support of this distribution is numerical values between 0 - 1, exactly the form of the response data in the prior elicitation task.
] 
We specify one of these distributions *a priori* to represent kinds of animals who *do not have* a stable causal mechanism that could give rise to the property (e.g., \textsc{lions} and \textsc{lay eggs}), which results in prevalence or prevalence values close to or equal to 0.
This "null distribution" is potentially present for all features in exactly the same way.
The second distribution represents kinds of animals who *do have* such a mechanism, and the two parameters of this distribution are not specified *a priori* and are not the same for all properties, but are inferred on a property-wise basis from participants' responses.
The *Mixture of Betas* distribution has a third free parameter (for each property), the relative contribution of the "null distribution" (for example: we expect the "null distribution" to not contribute at all to properties like *being female*, for which almost all categories have at least some members with the property).
To ensure the *Mixture of Betas* model of the prior is not overly complex, we fit an additional model that represents only a single underlying distribution (*Single Beta*) for a comparison.
<!-- is flexible and can represent different shapes for different properties (e.g., the differences in prevalence judgments for \textsc{lay eggs} vs. \text{has wings}). -->
For more details about model implementation and inference, see Appendix C.

@@

}
save(m.gen.endorse.priors.posteriorPredictive, file = '../analysis/generics-priors-posteriorPredictives.Rdata')

@@

gen.priors.cdfs <- m.gen.endorse.priors.posteriorPredictive %>%
  mutate(src = factor(src, levels = c("Data", "Structured", "Unstructured"),
                      labels = c("Empirical distribution", 
                                 "Mixture of Betas",
                                 "Single Beta"))) %>%
ggplot(.,
           aes( x = prevalence, color = src, lty = src))+
    #geom_density(aes(y = ..scaled..), adjust = 1.3, size = 1)+
    #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    stat_ecdf(size = 1)+
    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_alpha_manual(values = c(0.6, 0.4, 0))+
    facet_wrap(~Property, nrow = 2)+
    scale_linetype_manual(values = c(1, 4, 3))+
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    #coord_fixed()+
    xlab("prevalence") +
    ylab("Cumulative probability density")+
    theme(legend.title = element_blank(), legend.position = 'bottom')

@@

```{r generic-RSAmodels, fig.width = 8}
example.generics <- c("Tigers dont eat people", 
                      "Mosquitos carry malaria", 
                      "Robins lay eggs", 
                      "Robins are female",
                      "Leopards have spots")

n_chains <- 3
n_samples <- 100000
burn <- n_samples / 2
lg <- 20

model_prefix <- "results-generics-jointModel-S1-smntcs_"
#fixed_model_prefix <- "results-generics-jointModel-wNoise-inferFixedThresholdCts-20bins-S1-smntcs_some-"
# m.samp <- data.frame()
#m.samp.fixed <- data.frame()
#for (i in seq(1, n_chains)){
  #mi.gen <- fread(paste(project.path,  "models/generics/results/", model_prefix, "generic-",
  #                  n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
  #m.samp <- bind_rows(m.samp, mi.gen %>% mutate(chain = i))

#   mi.fixed <- fread(paste(project.path,  "models/generics/results/", fixed_model_prefix,
#                     n_samples, "_burn", burn, "_lag", lg ,"_chain", i, ".csv", sep = ""))
#   m.samp.fixed <- bind_rows(m.samp.fixed, mi.fixed %>% mutate(chain = i))
# }
# 
# save(m.samp,
#      file = paste(project.path,  "models/generics/results/", model_prefix, "generic-",
#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
#

# save(m.samp.fixed,
#      file = paste(project.path, "models/generics/results/results-generics-jointModel-S1-some-inferFixedThresholdCts-noise-100000_burn50000_lag20_2chains.RData", sep = ""))

     # file = paste(project.path,  "models/generics/results/", model_prefix, "some-",
    #                 n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))

@@

# load(file = paste(project.path,  "models/generics/results/", model_prefix, "some-",
#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))

# load(m.samp.fixed, 
#      file = paste(project.path, "models/generics/results/results-generics-jointModel-S1-some-inferFixedThresholdDisc-noise-100000_burn50000_lag20_2chains.RData", sep = ""))

load(file = paste(project.path, "models/generics/results/results-generics-jointModel-S1-some-inferFixedThresholdCts-noise-100000_burn50000_lag20_2chains.RData", sep = ""))

@@

uncertain.threshold.s1opt <- m.samp %>% 
  filter(type == "param") %>%
  group_by(param) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

fixed.threshold.s1opt <- m.samp.fixed %>% 
  filter(type == "param") %>%
  group_by(param) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

@@

```{r generic-endorsement-referent-prevalence-model, eval = F}
referentPrevalenceModel <- '
var model = function(){
  var g = uniformDrift({a:0, b: 1, width:0.2});
  var d = uniformDrift({a:0, b: 100, width:5});
  var betaParams = betaShape({g, d})
  var referentPrevDist = Beta(betaParams)
  mapData({data: preprocessedResponses}, function(d){
    observe(referentPrevDist, d)
  })
  return {g, d}
}
'
genericEndorsementRefPrevModel <- paste(genericEndorsementPriorModelHelpers, referentPrevalenceModel, sep = "\n")
```

```{r generic-referent-prevalence-model-run, eval = F}
m.gen.refprev.predictive <- data.frame()
n_samples <- 10000
lg = 0

for (p in example.generics ) {

  prevData <- d.prev %>% 
  mutate(sentence = paste(Category," " ,Property, sep = "")) %>%
  filter(sentence == p)

  m.gen.refprev <- webppl(genericEndorsementRefPrevModel,
                                 data = prevData$prevalence, data_var = "data",
                                 model_var = "model",
                                 chains = 1,
                                 cores = 1,
                                 inference_opts =
                                   list(method = "MCMC",
                                        samples = n_samples,
                                        burn = n_samples / 2,
                                        lag = lg,
                                        verbose = T))

    m.gen.refprev.predictive.item <- m.gen.refprev %>%
      group_by(Iteration, Chain) %>%
      spread(Parameter, value) %>%
      rowwise() %>%
      mutate(
        a = g*d,
        b = (1-g)*d,
        prevalence =rbeta(n = 1, shape1 = a,
                                 shape2 = b),
        Category = prevData[1,]$Category,
        Property = prevData[1,]$Property,
        src = "prevAloneModel"
      ) %>% ungroup()

    m.gen.refprev.predictive <- bind_rows(
      m.gen.refprev.predictive,
      m.gen.refprev.predictive.item %>%
        select( src, Category, Property, prevalence)
    )

}
#save(m.gen.endorse.priors.posteriorPredictive, file = '../analysis/generics-priors-posteriorPredictives.Rdata')
#head(prevData)
#n_samples
```

```{r gen-prev-forward, eval=F}
#Forward sample Target Prevalence from posterior on parameters (joint inference model)
m.samp.prev.params <- m.samp %>%
    filter(type == "targetPrevalence") %>%
    #filter(type == "withinKind") %>%
    mutate(parameter = paste(param, property, category, sep = "_")) %>%
    select(-param, -property, -category, -chain, -type) %>%
    #mutate(item = paste(parameter, property, sep = "_")) %>%
    group_by(parameter) %>%
    mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
    ungroup() %>%
    separate(parameter, into = c("parameter", "property", "category"), sep= "_")

m.samp.prevalence <- m.samp.prev.params %>%
    group_by(category, property, iteration) %>%
    spread(parameter, val) %>%
    rowwise() %>%
    mutate(
      a = mean*sampleSize,
      b = (1-mean)*sampleSize,
      prevalence = rbeta(n = 1, shape1 = a, shape2 = b)
      ) %>%
    ungroup()
```

```{r}
example.generics.properties <- c("dont eat people", 
                      "carry malaria", 
                      "lay eggs", 
                      "are female",
                      "have spots")
```

```{r gen-prev-dists, eval=F}
gen.prev.dists <- bind_rows(
  d.prev %>% 
  mutate(sentence = paste(Category," " ,Property, sep = "")) %>%
  filter(sentence %in% example.generics) %>%
  mutate(prevalence = prevalence / 100,
         src = 'data') %>% 
    select(-workerid, -trial_type),
  m.samp.prevalence %>% 
    mutate(sentence = paste(category," " ,property, sep = "")) %>%
    filter(sentence %in% example.generics) %>%
    select(property, category, prevalence) %>%
    rename(Category = category, Property = property) %>%
    mutate(src = 'model'),
  m.gen.refprev.predictive
)

ggplot(gen.prev.dists, aes( x = prevalence, color = src))+
  geom_density(aes( y = ..scaled.. ))+
    #  stat_ecdf(size = 1)+
  #geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
   #              position = position_dodge())+
  facet_wrap(~Property + Category, nrow = 1)+
  scale_color_solarized()+
  scale_x_continuous(limits = c(-0.05,1.05), breaks = c(0, 0.5, 1)) +
  scale_y_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
  theme(strip.text.y = element_text(angle = 0))
```

```{r generic-model-scatters, cache = F}
m.gen.endorse.rsa <- bind_rows(
  left_join(
    d.gen.endorse.bayes,
    m.gen.fullmodel.endorsement %>%
      mutate(sentence = paste(category, " ", property, ".", sep = "")) %>%
      ungroup() %>%
      select(-type, -param)
  ) %>%
    mutate(src = "generics_model"),
  left_join(
    d.gen.endorse.bayes,
    m.gen.somemodel.endorsement %>%
      mutate(sentence = paste(category, " ", property, ".", sep = "")) %>%
      ungroup() %>%
      select(-type, -param)
  ) %>%
    mutate(src = "some_model")
)

@@

generics.endorsement.models <- bind_rows(
  d.gen.endorse.regression,
  left_join(
    m.gen.endorse.rsa %>% 
      rename(prediction_mean = MAP, prediction_ci_lower = cred_lower, prediction_ci_upper = cred_upper),
    d.gen.endorse.regression %>% 
      select(sentence, Property, Category, prev_mean, cv_mean)
  )
) %>%
  mutate(src = factor(src, levels = c( "some_model",
                                      "generics_model",
                                      "regression_Prev", 
                                      "regression_Prev_Cuevalidity"
                                     ),
                      labels = c("Fixed semantics model",
                                 "Uncertain semantics model",
                                 "Prevalence",
                                 "Cue validity + Prevalence"
                                 ))) %>%
  ggplot(., aes ( x = prediction_mean, xmin = prediction_ci_lower, xmax = prediction_ci_upper,
                  y = MAP_h, ymin = low, ymax = high, fill = prev_mean ))+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  geom_linerange(alpha = 0.4)+
  geom_errorbarh(alpha = 0.4)+
  geom_point(shape = 21, size = 3)+
  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
  coord_fixed()+
  xlab("Model prediction")+
  ylab("Human generic endorsement")+
  facet_wrap(~src, nrow = 2)+
  #theme(legend.position = "bottom")+
  guides(fill = F)
```

```{r generic-model-insets, fig.width = 4.75, fig.height = 1.5}

@@

To evaluate the fixed-threhsold model, we examine the posterior distribution which represents what we should believe about the latent parameters of the model (referent prevalence, prevalence priors, the optimality, fixed-threshold, and noise parameters) given the observed data, as well as what predictions of the model given these parameter values.
The Maximum A-Posteriori value and 95\% highest probability density interval for the inferred (fixed) threshold and noise parameters are `r round(fixed.threshold.posterior[[1,"MAP"]], 2)` [`r round(fixed.threshold.posterior[[1,"cred_lower"]], 2)`,
`r round(fixed.threshold.posterior[[1,"cred_upper"]], 2)`] and `r round(generics.fixed.noise.posterior[[1,"MAP"]], 2)` [`r round(generics.fixed.noise.posterior[[1,"cred_lower"]], 2)`,
`r round(generics.fixed.noise.posterior[[1,"cred_upper"]], 2)`], respectively.
The inferred optimality parameter in Eq. \ref{eq:S1} is `r round(fixed.threshold.s1opt[[1,"MAP"]], 2)` [`r round(fixed.threshold.s1opt[[1,"cred_lower"]], 2)`, `r round(fixed.threshold.s1opt[[1,"cred_upper"]], 2)`].

@@

We first examine the posterior predictive distribution on the prevalence prior and referent-prevalence data to ensure that the joint-inference model fits these data as well as the Bayesian model that modeled these data in isolation.
This is an important step in model validation because it tells us that our model's predictions are derived from reasonable values of the parameters.
Importantly, the model recapitulates the prior elicitation data (e.g., the probability of laying eggs among various species) and the referent-category prevalence data (e.g., the probability of laying eggs among robins) as it did when the Bayesian data analysis model only included these data and their associated model (results section of Expt. 1b).
This result confirms that the theoretically-interesting predictions of this model --- predictions of generic endorsement --- are based on intuitively meaningful model components (i.e., the shapes of the prevalence distributions).

The inferred optimality parameter in Eq. \ref{eq:S1} is `r round(fixed.threshold.s1opt[[1,"MAP"]], 2)` [`r round(fixed.threshold.s1opt[[1,"cred_lower"]], 2)`, `r round(fixed.threshold.s1opt[[1,"cred_upper"]], 2)`].
